Finding the True MVP

### 2024-12-14 paper/paper.qmd
Formatting Edits

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-mvpindex
#| fig-cap: "MVP index of of Historical and simulated MVPs"

@@

# Create the faceted plot with lines connecting points
ggplot(merged_data, aes(x = Year, y = MVP_index, group = Source)) +
  geom_line(aes(color = Source), size = 1, alpha = 0.7) +  # Add lines connecting points
  geom_point(aes(color = Source), size = 3, alpha = 0.7) +  # Keep the points
  facet_wrap(~ Source, ncol = 2) +  # Facet by the Source column, side by side
  labs(
    title = "Scatter: Year vs. MVP Index",
    x = "Year",
    y = "MVP Index"
  ) +
  coord_cartesian(ylim = c(1.7, 2.8)) +  # Maintain the same y-axis range
  theme_minimal() +
  theme(
    legend.position = "none",  # Remove the legend since it's redundant with faceting
    strip.text = element_text(size = 12, face = "bold")
  )

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-pts
#| fig-cap: "MVP PPG over Time"

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-reb
#| fig-cap: "MVP RPG over Time"

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-ast
#| fig-cap: "MVP ASG over Time"

@@

## Weaknesses and next steps {#sec-weak}

@@

To examine the robustness of MVP outcomes, simulations were conducted to evaluate how changes to the voting methodology could influence results. For instance, adjusting the weight given to statistical performance in vote tallies revealed several seasons where the MVP Index-aligned winner differed from the historically selected MVP. Similarly, experimenting with alternative weighting schemes, such as assigning equal points for all top-five rankings instead of a tiered system, led to notable shifts in the final outcomes. These simulations highlight the significant role that methodological choices play in shaping MVP selections, showing that even small adjustments can result in different winners. By simulating different voting scenarios, it becomes clear that the current system is sensitive to how votes are counted and weighted, underscoring the need for transparency and careful consideration of methodology.

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-mvpindex
#| fig-cap: "MVP index of Historical and simulated MVPs"

@@

# Create the faceted plot with lines connecting points
ggplot(merged_data, aes(x = Year, y = MVP_index, group = Source)) +
  geom_line(aes(color = Source), size = 1, alpha = 0.7) +  # Add lines connecting points
  geom_point(aes(color = Source), size = 3, alpha = 0.7) +  # Keep the points
  facet_wrap(~ Source, ncol = 2) +  # Facet by the Source column, side by side
  labs(
    x = "Year",
    y = "MVP Index"
  ) +
  coord_cartesian(ylim = c(1.7, 2.8)) +  # Maintain the same y-axis range
  theme_minimal() +
  theme(
    legend.position = "none",  # Remove the legend since it's redundant with faceting
    strip.text = element_text(size = 12, face = "bold")
  )

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-pts
#| fig-cap: "PPG of Historical and simulated MVPs"

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-reb
#| fig-cap: "RPG of Historical and simulated MVPs"

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-ast
#| fig-cap: "APG of Historical and simulated MVPs"

@@

## Weaknesses and Next Steps {#sec-weak}

@@

To examine the robustness of MVP outcomes, simulations were conducted to evaluate how changes to the voting methodology could influence results. For instance, adjusting the weight given to statistical performance in vote tallies revealed several seasons where the MVP Index-aligned winner differed from the historically selected MVP. Similarly, experimenting with alternative weighting schemes, such as assigning equal points for all top-five rankings instead of a tiered system, led to notable shifts in the final outcomes. These simulations highlight the significant role that methodological choices play in shaping MVP selections, showing that even small adjustments can result in different winners. By simulating different voting scenarios, it becomes clear that the current system is sensitive to how votes are counted and weighted, emphasising the need for transparency and careful consideration of methodology.
